Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
Intro to ALG3

\medskip
\noindent
\textbf{Algorithmic techniques.} The variant for general $k$ is still unresolved, hence it is vital to summarize algorithmic techniques used in this paper.
A straightforward analysis of the algorithm from Section~\ref{sec:k3} results in the bound $O(\ell^2)$, and the analysis must be improved in two places. One must bound the cost of each of $O(\ell)$ reconfigurations in~phase by a~constant, and show that the optimum offline algorithm must pay for a~significant portion of inter-cluster requests \maciek{how to concisely say that there is also a~migrate possibilty}.
We bound the cost of the latter by estimating the capabilities of the optimum offline algorithm to \emph{prepare} for an incoming sequence of requests.
Furthermore, in the analysis of the algorithm from Section~\ref{sec:k2}, we propose a~novel charging scheme for edges that share a~vertex.

@@

\maciek{Intro is missing.}
\maciek{
	A straightforward analysis of the algorithm from Section~\ref{sec:k3} results in the bound $O(\ell^2)$, and the analysis must be improved in two places. One must bound the cost of each of $O(\ell)$ reconfigurations in a~phase by a~constant, and show that the optimum offline algorithm must pay for a~significant portion of inter-cluster requests.
	We bounded the cost of the latter by estimating the capabilities of the optimum offline algorithm to \emph{prepare} for an incoming sequence of requests.}

@@

In our analysis, we distinguish among three types of clusters: $C_1, C_2, C_3$. In a~cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that upper bounds the cost of a~single repartition of \TAlg.

>>>>

\medskip
\noindent
\textbf{Algorithmic techniques.} The variant for general $k$ is still unresolved, hence it is vital to summarize algorithmic techniques used in this paper.
A straightforward analysis of the algorithm from Section~\ref{sec:k3} results in the bound $O(\ell^2)$, and the analysis must be improved in two places. One must bound the cost of each of $O(\ell)$ reconfigurations in~phase by a~constant, and show that the optimum offline algorithm must pay significant cost for inter-cluster requests.
We bound the cost of the latter by estimating the capabilities of the optimum offline algorithm to \emph{prepare} for an incoming sequence of requests.
Furthermore, in the analysis of the algorithm from Section~\ref{sec:k2}, we propose a~novel charging scheme for edges that share a~vertex.

@@

The proposed algorithm is a modified version of the algorithm DET proposed by Avin et al.~\cite{repartition-disc}, that for $k=3$ is $O(\ell^2)$-competitive.
In our algorithm, we choose the closest partition after a component merge instead of an arbitrary one.
This allows to bound the cost of repartition by a constant (Lemma~\ref{lem:1req}).

This modification alone is insufficient to obtain $O(\ell)$-competitive algorithm, and the analysis must be further improved.
In particular, pairs of nodes that did not reach the collocation threshold $\alpha$ (called external requests) incur the cost $O(\ell^2)$ for the algorithm in each phase.
The novel part of the analysis lower-bounds the cost of \OPT on external requests, while considering its savings from migrations and possibly different configuration at the beginning of the phase.
This way, we show that \OPT paid a significant portion of the algorithm's cost on external requests.

@@

In our analysis, we distinguish among three types of clusters: $C_1, C_2$ and $C_3$. In a~cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that upper bounds the cost of a~single repartition of \TAlg.
